Chapter 02: Our first model,Grand Old Logistic Regression

### 2020-09-15 DATA622/M02-glm.rmd
Updated path variables

#Load input data heart.csv and ecoli.csv
```{r MainCode}
unixpath<-"/home/data/ML.Data/heart.csv"
unixecolipath<-"/home/data/ML.Data/ecoli.csv"
path<-"c://Users/rkannan/rk/data/heart.csv"
ecolipath<-"c://Users/rkannan/rk/data/ecoli.csv"
heart<-read.csv(path,header=TRUE,sep=',',stringsAsFactors=FALSE)
ecoli<-read.csv(ecolipath,head=T,sep=',',stringsAsFactors=F)
```
Let us write a one-line utility function to read in a CSV as above
We assume, comma separated and includes a header record.
```{r}
loadData<-function(csvfile) { read.csv(csvfile,head=T,sep=',',stringsAsFactors=F) }
ecoli_1<-ecoli
ecoli_2<-loadData(ecolipath)
TBL=table(ecoli_1==ecoli_2)
TBL
```
## Review the data, quick and easy EDA
View a few records (head/tail), dimension, number of rows and records
and the variable names.
Everything is an object and mostly a list. We can index into a list to 
access the elements in the list. R index runs from 1 to the length.
```{r}
head(heart)
```
### unix head and tail commands
R commands *head* and *tail* are like the Unix head and tail shell commands
These commands output a few records from the beginning or at the end of the file.
```{r}
tail(heart)
```
### What is the shape of this dataset
How many  observations does it have (each row is an observation)
How many variables are available to us -- number of columns

>>>>

#Load input data heart.csv and ecoli.csv
```{r MainCode}
unixpath<-"/home/data/ML.Data/heart.csv"
unixecolipath<-"/home/data/ML.Data/ecoli.csv"
#path<-"c://Users/rkannan/rk/data/heart.csv"
#ecolipath<-"c://Users/rkannan/rk/data/ecoli.csv"
path<-"heart.csv"
ecolipath<-"ecoli.csv"
heart<-read.csv(path,header=TRUE,sep=',',stringsAsFactors=FALSE)
ecoli<-read.csv(ecolipath,head=T,sep=',',stringsAsFactors=F)
```
Let us write a one-line utility function to read in a CSV as above
We assume, comma separated and includes a header record.
```{r}
loadData<-function(csvfile) { read.csv(csvfile,head=T,sep=',',stringsAsFactors=F) }
ecoli_1<-ecoli
ecoli_2<-loadData(ecolipath)
TBL=table(ecoli_1==ecoli_2)
TBL
```
## Review the data, quick and easy EDA
View a few records (head/tail), dimension, number of rows and records
and the variable names.
Everything is an object and mostly a list. We can index into a list to 
access the elements in the list. R index runs from 1 to the length.
```{r}
head(heart)
```
### unix head and tail commands
R commands *head* and *tail* are like the Unix head and tail shell commands
These commands output a few records from the beginning or at the end of the file.
```{r}
tail(heart)
```
### What is the shape of this dataset
How many  observations does it have (each row is an observation)
How many variables are available to us -- number of columns
